\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
added some info about the dionaea logs

>>>>

\subsection{Dionaea}
As mentioned in Section \ref{Setup} Dionaea runs several services. In the table below we will show how many times those services got connected.

\begin{tabular}{|l|c|r|}
\hline
Service & Port & Number of connections \\ \hline
MSSQL  & 1433 & 1632 \\ \hline
MS SMB filesharing & 445 & 67 \\ \hline
FTP & 21 & 55 \\ \hline
MySQL & 3306 & 54 \\ \hline
Session Initiation Protocol & 5060 & 9 \\ \hline
\end{tabular}

As we looked further into the Dionaea logfiles we found that MSSQL was connected to from 95.82.11.28, which is in Iran, 1414 times. However, the SMB filesharing, FTP and SIP were mostly connected from one IP, namely 130.89.165.58. This IP is from Twente University, so probably it was another student.
